\documentclass{article}
\begin{document}
We will do the ultimate smackdown of these two algorithms!
\subsection{Time Complexity}
\subsubsection{Merge Sort}
Merge sort uses recursion with $O( \log n)$ layers and 
$O(n/2^{\log l - 1})$ splits per layer making the part 
where it splits into sets be $O(n)$. The merging process 
is $O(n + m)$ with $n, m$ being the sizes of the lists to 
merge so it is the sum of all these - $O(n)$ per layer 
times $O(\log n)$ layers giving Merge Sort 
an $O(n \log n)$ time complexity!
\subsubsection{Bubble Sort}
Bubble Sort has an $O(n^2)$ time complexity from repeately bubbling up 
maximums.
\subsubsection{Scoring}
The win for time complexity goes to... MERGE SORT! \newline
The score is $1 - 0$, Merge Sort
\subsection{Memory Complexity}
\subsubsection{Merge Sort}
Merge Sort uses $O(n)$ auxilary memory, as the merging process is $O(n + m)$ in time and memory.
\subsubsection{Bubble Sort}
Bubble Sort uses $O(1)$ when bubbling up.
\subsubsection{Scoring}
Bubble Sort gets a huge W here, making it tie game at $1 - 1$. It's a close race, and stability is the tiebreak!
\subsection{Stability}
\subsubsection{Merge Sort}
Every part including the merging process is stable, so Merge Sort is stable!
\subsubsection{Bubble Sort}
Bubble Sort is stable, as the process of "bubbling up" is stable.
\subsubsection{Scoring}
It's tied, leaving us at $1.5 - 1.5$!
\subsection{Tiebreaks and Algorithm Grades}
Time complexity is the most important thing for a sorting algorithm, 
giving Merge Sort the tiebreak! It's so important that Merge Sort gets 
a \textbf{A-} due to memory complexity, but Bubble Sort being so slow 
gives it a \textbf{C+}. 
\end{document}